### 2012-02-21 latex/modelo_fisico.tex

\begin{equation}
\boxed{\begin{aligned}&\dot{x}=v_{q_z\prime} \cos \varphi \cos \theta + v_{q_y\prime} ( \cos \theta \sin \varphi \sin \psi-\cos \varphi \sin \theta ) + v_{q_z\prime}(\sin \psi \sin \theta + \cos \psi \cos \theta \sin \varphi)\\
&\dot{y}=v_{q_z\prime} \cos \varphi \sin \theta + v_{q_y\prime} (\cos \psi \cos \theta + \sin \theta \sin \varphi \sin \psi) + v_{q_z\prime}( \cos \psi \sin \theta \sin \varphi-\cos \theta \sin \psi )\\
&\dot{z}= -v_{q_z\prime} \sin \varphi  + v_{q_y\prime} \cos \varphi \sin \psi  + v_{q_z\prime}\cos \varphi \cos \psi\\
&\dot{\psi}=\omega_{q_x\prime} + \omega_{q_z\prime}\tan\varphi \cos\psi + \omega_{q_y\prime}\tan\varphi \sin\psi\\
&\dot{\varphi}=\omega_{q_y\prime}\cos \psi - \omega_{q_z\prime}\sin\psi\\
&\dot{\theta}=\omega_{q_z\prime} \frac{\cos\psi}{\cos\varphi}  + \omega_{q_y\prime}\frac{\sin\psi}{\cos\varphi}\\
&\dot{v_{q_z\prime}}=v_{q_y\prime} \omega_{q_z\prime} - v_{q_z\prime} \omega_{q_y\prime}+Mg\sin\varphi\\
&\dot{v_{q_y\prime}}=v_{q_z\prime} \omega_{q_x\prime} - v_{q_z\prime} \omega_{q_z\prime}-Mg\cos\varphi\sin\psi\\
&\dot{v_{q_z\prime}}=v_{q_z\prime} \omega_{q_y\prime} - v_{q_y\prime} \omega_{q_x\prime}-Mg\cos\varphi\cos\psi+\sum_{i=1}^4T_i\\
&\dot{\omega_{q_x\prime}}=\frac{\omega_{q_y\prime}\omega_{q_z\prime}(I_{yy}-I_{zz})+\omega_{q_y\prime}I_{zz_m}(\omega_1-\omega_2+\omega_3-\omega_4)}{I_{xx}}+\frac{L(T_2-T_4)}{I_{xx}}\\
&\dot{\omega_{q_y\prime}}=\frac{\omega_{q_x\prime}\omega_{q_z\prime}(-I_{xx}+I_{zz})+\omega_{q_x\prime}I_{zz_m}(\omega_1-\omega_2+\omega_3-\omega_4)}{{I_yy}}+\frac{L(T_3-T_1)}{I_{yy}}\\
&\dot{\omega_{q_z\prime}}=\frac{-I_{zz_m}(\dot{w_1}-\dot{w_2}+\dot{w_3}-\dot{w_4})}{I_{zz}}+\frac{Q_1-Q_2+Q_3-Q_4}{I_{zz}}\\
\end{aligned}}
\end{equation}

>>>>

\begin{equation}
\boxed{\begin{aligned}&\dot{x}=v_{q_z\prime} \cos \varphi \cos \theta + v_{q_y\prime} ( \cos \theta \sin \varphi \sin \psi-\cos \varphi \sin \theta ) + v_{q_z\prime}(\sin \psi \sin \theta + \cos \psi \cos \theta \sin \varphi)\\
&\dot{y}=v_{q_z\prime} \cos \varphi \sin \theta + v_{q_y\prime} (\cos \psi \cos \theta + \sin \theta \sin \varphi \sin \psi) + v_{q_z\prime}( \cos \psi \sin \theta \sin \varphi-\cos \theta \sin \psi )\\
&\dot{z}= -v_{q_z\prime} \sin \varphi  + v_{q_y\prime} \cos \varphi \sin \psi  + v_{q_z\prime}\cos \varphi \cos \psi\\
&\dot{\psi}=\omega_{q_x\prime} + \omega_{q_z\prime}\tan\varphi \cos\psi + \omega_{q_y\prime}\tan\varphi \sin\psi\\
&\dot{\varphi}=\omega_{q_y\prime}\cos \psi - \omega_{q_z\prime}\sin\psi\\
&\dot{\theta}=\omega_{q_z\prime} \frac{\cos\psi}{\cos\varphi}  + \omega_{q_y\prime}\frac{\sin\psi}{\cos\varphi}\\
&\dot{v_{q_z\prime}}=v_{q_y\prime} \omega_{q_z\prime} - v_{q_z\prime} \omega_{q_y\prime}+g\sin\varphi\\
&\dot{v_{q_y\prime}}=v_{q_z\prime} \omega_{q_x\prime} - v_{q_z\prime} \omega_{q_z\prime}-g\cos\varphi\sin\psi\\
&\dot{v_{q_z\prime}}=v_{q_z\prime} \omega_{q_y\prime} - v_{q_y\prime} \omega_{q_x\prime}-g\cos\varphi\cos\psi+\frac{1}{M}\sum_{i=1}^4T_i\\
&\dot{\omega_{q_x\prime}}=\frac{\omega_{q_y\prime}\omega_{q_z\prime}(I_{yy}-I_{zz})+\omega_{q_y\prime}I_{zz_m}(\omega_1-\omega_2+\omega_3-\omega_4)}{I_{xx}}+\frac{L(T_2-T_4)}{I_{xx}}\\
&\dot{\omega_{q_y\prime}}=\frac{\omega_{q_x\prime}\omega_{q_z\prime}(-I_{xx}+I_{zz})+\omega_{q_x\prime}I_{zz_m}(\omega_1-\omega_2+\omega_3-\omega_4)}{{I_yy}}+\frac{L(T_3-T_1)}{I_{yy}}\\
&\dot{\omega_{q_z\prime}}=\frac{-I_{zz_m}(\dot{w_1}-\dot{w_2}+\dot{w_3}-\dot{w_4})}{I_{zz}}+\frac{Q_1-Q_2+Q_3-Q_4}{I_{zz}}\\
\end{aligned}}
\end{equation}
